---
title: "Chignik Sockeye 2019-2020 Re-analysis with 2020 Baseline"
output:
  html_notebook:
    theme: united
    toc: yes
editor_options: 
  chunk_output_type: inline
---

# Purpose

This inseason analysis serves two purposes:  

  1) Re-analyze 2019-2020 inseason samples against the *new* baseline (2020) with 16 populations and the 2 new RAD loci,
  2) Compare the stock composition estimates to the previous baseline (2018).
  
The *BAYES* baseline update was described in `../../../Baseline/2020/`

This *R Notebook* will perform the following tasks:  

  * Re-create 2019-2020 *BAYES* control files for 2020 baseline "Chignik16pops22RAD_develop"
  * Summarize stock composition estimates
  * Compare stock composition estimates to the results from the 2018 baseline

# Background

This project estimates the stock composition of early- and late-run sockeye salmon through the Chignik weir to estimate the transition between the two runs in the escapement.

At the end of 2018 (after that year's inseason), we did a baseline update to include 2 of Wes Larson's "Islands of Divergence" RAD SNPs and to revisit previous pooling. This baseline update was largely done by Chase as his first baseline, and by accident fish missing 20% or more loci were not removed from the 2018 baseline that was used for 2019-2020 inseason. I (Kyle) noticed this error while using the Chignik baseline to test the BAYES functions in GCL 2.0 and redid the baseline with those new 2.0 functions. The main difference in this *new* 2020 baseline is that it has 17 fewer fish due to those missing fish and some additional duplicates found due to how the new functions work (uses *rubias* dupcheck).

*NOTE* This notebook is using the **new** GCL 2.0 functions from the  `develop` branch!!!

# Setup

Load packages and source GCL functions.
```{r load_source}
rm(list = ls())

library(tidyverse)
library(lubridate)
library(rubias)

source("~/../R/Functions.GCL.R")

load_objects(path = "../../2019/Objects")
load_objects(path = "../../2020/Objects")
load_objects(path = "../../../Baseline/2020/Objects_new_functions_develop/")
# load_objects(path = "../../2020/rubias/baseline")
```

# Re-create Control files

## Directories

Create a new directory for the 2020 baseline *BAYES* control files
```{r}
dir.create("../../2019/BAYES/Control_2020baseline_develop")
dir.create("../../2020/BAYES/Control_2020baseline_develop")
```

## Testing

Read in a control file
```{r}
(x <- read.table(file = "../../2019/BAYES/Control/Done/SCHIG19_1Chain1.ctl", sep = "\n"))
```

Update second row with new baseline file name
```{r}
x[2, 1] <- "Chignik16pops22RAD_develop.bse"
x
```

Write out
```{r}
write.table(
  x = x,
  file = "../../2019/BAYES/Control_2020baseline_develop/SCHIG19_1Chain1.ctl",
  quote = FALSE,
  row.names = FALSE,
  col.names = FALSE
)
```

Comparing this updated control file to the OG, it looks like this worked! Now time to create a function to whip through them all!

## Function

### 2019

```{r}
og_dir <- "../../2019/BAYES/Control/Done/"
new_dir <- "../../2019/BAYES/Control_2020baseline_develop/"
filename <- list.files(path = og_dir)

sapply(filename, function(ctrl) {
  x <- read.table(file = paste0(og_dir, ctrl), sep = "\n")
  x[2, 1] <- "Chignik16pops22RAD_develop.bse"
  write.table(
    x = x,
    file = paste0(new_dir, ctrl),
    quote = FALSE,
    row.names = FALSE,
    col.names = FALSE
  )
})
```

### 2020

```{r}
og_dir <- "../../2020/BAYES/Control/Done/"
new_dir <- "../../2020/BAYES/Control_2020baseline_develop/"
filename <- list.files(path = og_dir)

sapply(filename, function(ctrl) {
  x <- read.table(file = paste0(og_dir, ctrl), sep = "\n")
  x[2, 1] <- "Chignik16pops22RAD_develop.bse"
  write.table(
    x = x,
    file = paste0(new_dir, ctrl),
    quote = FALSE,
    row.names = FALSE,
    col.names = FALSE
  )
})
```

# Re-summarize

## 2018 Baseline

### 2019

```{r}
load_objects(pattern = "chignik_2019_dates.bayes", path = "../../2019/Estimates objects/")
chignik_2019_dates.bayes
```

### 2020

```{r}
load_objects(pattern = "chignik_2020_dates.bayes", path = "../../2020/Estimates objects/")
chignik_2020_dates.bayes
```

## 2020 Baseline

### 2019

```{r}
SCHIG19_estimates_2020baseline <- 
  CustomCombineBAYESOutput.GCL(
    groupvec = 1:2, 
    groupnames = ChignikGroups, 
    maindir = "../../2019/BAYES/Output_2020baseline_develop/", 
    mixvec = sillys_strata_2019,
    prior = "", 
    ext = "RGN", 
    nchains = 5, 
    burn = 0.5, 
    alpha = 0.1, 
    PosteriorOutput = FALSE)
```

Bind everything together
```{r summary_all_year_run1}
(chignik_2019.bayes_2020baseline <-
   bind_rows(sapply(sillys_strata_2019, function(mix) {
     as_tibble(cbind(SCHIG19_estimates_2020baseline[[mix]], "repunit" = ChignikGroups, silly = mix))
   }, simplify = FALSE)))
```
``

### Compare

```{r}
chignik_2019.bayes_2020baseline %>% 
  filter(repunit == "Black Lake") %>% 
  select(silly, mean, `5%`, `95%`)
```

```{r}
chignik_2019_dates.bayes %>% 
  filter(repunit == "Black Lake") %>% 
  select(silly, strata, mean, `5%`, `95%`)
```

### 2020

```{r}
SCHIG20_estimates_2020baseline <- 
  CustomCombineBAYESOutput.GCL(
    groupvec = 1:2, 
    groupnames = ChignikGroups, 
    maindir = "../../2020/BAYES/Output_2020baseline_develop/", 
    mixvec = sillys_strata_2020,
    prior = "", 
    ext = "RGN", 
    nchains = 5, 
    burn = 0.5, 
    alpha = 0.1, 
    PosteriorOutput = FALSE)
```

Bind everything together
```{r}
(chignik_2020.bayes_2020baseline <-
   bind_rows(sapply(sillys_strata_2020, function(mix) {
     as_tibble(cbind(SCHIG20_estimates_2020baseline[[mix]], "repunit" = ChignikGroups, silly = mix))
   }, simplify = FALSE)))
```
``

### Compare

```{r}
chignik_2020.bayes_2020baseline %>% 
  filter(repunit == "Black Lake") %>% 
  select(silly, mean, `5%`, `95%`)
```

```{r}
chignik_2020_dates.bayes %>% 
  filter(repunit == "Black Lake") %>% 
  select(silly, strata, mean, `5%`, `95%`)
```

# Conclusions

In conclusion, only 2 out of 12 mixtures moved by 1%, all others were less. Great news, the "new" 2020 baseline isn't too different than what we've been using for the past 2 years (2019/2020), no need to freak out and update Westward Region Staff, we'll just use the 2020 baseline next year ;)